My title

### 2022-03-21 outputs/paper/paper.Rmd
Update subtitle for cross-compare plots

It seems like samples with University Education have higher chance of getting "Sexual Assault" and "Theft of personal property".

@@

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data,
                      col1 = "eor_01c", col2 = "msvic",
                      col1_num=eor_01c_num, col1_labels=eor_01c_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="University Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime",
                      plot_ylab="Percentage", 
                      plot_fill_lab="University Education")
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eor_01b < 3),
                      col1 = "eor_01b", col2 = "msvic",
                      col1_num=eor_01b_num, col1_labels=eor_01b_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="College Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime", 
                      plot_ylab="Percentage", 
                      plot_fill_lab="college Education")
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eor_01a < 3),
                      col1 = "eor_01a", col2 = "msvic",
                      col1_num=eor_01a_num, col1_labels=eor_01a_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="Elementary School Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime", 
                      plot_ylab="Percentage",
                      plot_fill_lab="Elementary School Education")
```

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eduf10 < 6),
                            col1 = "edum5", col2 = "msvic",
                      col1_num=eduf10_num, col1_labels=eduf10_labels,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="Father Education VS Crime", 
                      plot_subtitle="Sex Discrimination has an obvious correlation with Sexual Assault", 
                      plot_xlab="Crime", 
                      plot_ylab="Percentage of Father Education", 
                      plot_fill_lab="Education")
```

>>>>

It seems like samples with University Education have higher chance of getting "Sexual Assault", "Vandalism" "Theft of household property".
Higher "Theft of household property" and "Vandalism" count can be easily explained by, people with higher education may have higher income (higher household property value) which could attract theft.

I couldn't find a good explanation high "Sexual Assault" for university-education population.

## Discrimination VS Crime

@@

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eduf10 < 6),
                            col1 = "edum5", col2 = "msvic",
                      col1_num=eduf10_num, col1_labels=eduf10_labels,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="Father Education VS Crime", 
                      plot_subtitle="Relatively low crime rate for all crimes", 
                      plot_xlab="Crime", 
                      plot_ylab="Percentage of Father Education", 
                      plot_fill_lab="Education")
```
